\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=0.5in,bmargin=0.75in,lmargin=0.5in,rmargin=0.5in}
\usepackage{color}
\usepackage{array}
\usepackage{calc, framed}
\usepackage{amsmath}
\usepackage{setspace, multicol, graphicx}
\usepackage{esint}
\onehalfspacing

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\pagestyle{empty}

\makeatother

\usepackage{babel}
\begin{document}
\textbf{\Large }%
\begin{tabular}{>{\raggedright}p{5cm}>{\raggedleft}p{12.85cm}}
\textbf{\Large \hspace{-10mm}MATH 3134} & Homework Assignment 1\\
Due: Friday, August 28, 2020\\
Introduction Assignment\tabularnewline
\end{tabular}{\Large \par}
\begin{enumerate}
\item\hspace*{0mm}[13pts] At the beginning of each semester, I have students write a letter or make a video to me answering the questions listed below. \\ The purpose of these letters is two-fold.  They allow me to get to know you and they allow me to construct examples that are relevant to the interests of the class.\\
Please spend some time thinking about your answers.

\noindent Please answer the following questions:
\begin{enumerate}
\item What is your major?  What are potential careers that you are interested in?
\item What college level math courses have you taken? Where did you take them?
\item What do you like about math and the way it is presented?
\item What do you dislike about math and the way it is presented? (For example, I had one student say the following: ``I like mathematics, but I hate when teachers nitpick answers for no reason.  I also hate how all math classes are super boring.")\\  Please be honest in your answer because you will not offend me.  
\item What is your personal process for completing homework assignments?  What do you do when you get stuck on a problem?
\item Why you are taking Applied Combinatorics? (If it is required, please note whether or not you understand why this particular course is required by your major.)
\item Give at least one interesting topic in Combinatorics that you hope that we will cover.  If you are not familiar with the content of Combinatorics, then do a quick Google search and see if any of the information that pops up seems interesting.
\item How are you coping with the pandemic and the transition to mostly online learning?
\item Have you ever taken Applied Combinatorics before?  If you are retaking the course, then how can I better help you learn the material?
\item How comfortable do you feel writing a program? What language do you feel most comfortable using? Please note that no programming experience is required for this course.
\item How comfortable do you feel with proof by contradiction?  Proof by contrapositive?  Inductive proof?\\
Note that I have posted some old lecture notes on these topics to Canvas.
\item What are your favorite books? TV shows? movies?
\item What is your favorite song right now?
\item What are your hobbies?  Do you play any sports? Are you involved in any clubs/organizations on campus?  
\end{enumerate}
Feel free to include any other interesting information about yourself.  \\


How do you submit this?
\begin{itemize}
\item Make a video and upload it to Canvas.  This is my preferred option, as I believe it will help me get to know you better.
\item You may type or handwrite a letter answering the questions above, which you may submit as a PDF on Canvas.
\end{itemize}






\end{enumerate}

\end{document}
