\documentclass{article}
\usepackage[utf8]{inputenc}

\title{homework1}
\author{Doris Su (PID: guanang)}
\date{August 2020}

\begin{document}

\maketitle

\section{Introduction}

\renewcommand{\labelenumi}{(\alph{enumi})}

\begin{enumerate}
\item My major is Controls, Robotics and Autonomy, a new field in Engineering. I am intended and interested in doing biomedical robots in the future. 

\item I have finished MATH2204, 2214 and 2534 in VT.

\item I like the logic and the clear path to show the way of approaching problem.

\item I dislike memorizing concepts sometimes. It is unclear to show the supported way to get the conclusion of an item and pretty complex.   

\item After listening and taking notes, I would first complete the problem on my own. After the 'first finish', I will look over notes and textbook for the uncertain parts. If I got stuck, I would search for the Internet for a similar problem for solution or ask teacher for help sometimes. 

\item I am thinking about to have MATH minor since it is important for engineering students to have a solid foundation of math. Combinatorics seems not pretty difficult and also helpful with better understanding for coding techniques. 

\item Maybe order theory. 

\item Even though I am not pretty comfortable with online learning since I believe in-person learning would be more concentrate in class and easy to ask questions, I would prefer to go online since I don't want to be sick. Additionally, with the recorded video and zoom office hour, there are more chances to check for learning process with unlimited time of watching videos.

\item Never.

\item As a computer engineering student, I am fine with writing code. The language I am familiar with is C++ and python. Also limited experience with matlab and mathematica. I have no experience with Latex. 

\item I think I will work fine with these proof.

\item The kite runner is my favorite book. My favorite TV shows are SHIELDS and Doctor House. For the movies, marvel is my favorite series of movies.

\item All songs from Burno Mars and Taylor Swift.

\item My hobbies are about sports mainly,like skateboarding and skiing. I am in the robot club in ECE department currently and used to be in inVent Rocketry organization.   

\end{enumerate}

\end{document}
